% !TEX program = xelatex % (can also use "lualatex")
\documentclass[11pt,a4paper]{moderncv}

\moderncvstyle[left,details,symbols]{classic}
\moderncvcolor{blue}

\renewcommand*{\sectionfont}{\LARGE}
\renewcommand{\baselinestretch}{1.05}

% Personal data
\name{Laurens}{van der Tas}
\title{Senior Cloud Data Platform \& MLOps Engineer}
\address{Rotterdam, South Holland, Netherlands}{}{}
\homepage{lpvdt.github.io}
\social[linkedin]{lpvdt}
\social[github]{LPvdT}
\email{laurens.vandertas@gmail.com}

%----------------------------------------------------------------------------------
%           Content
%----------------------------------------------------------------------------------
\begin{document}

\hypersetup{
  pdftitle={Laurens van der Tas - CV},
  pdfauthor={Laurens van der Tas},
  pdfsubject={Senior Cloud Data Platform \& MLOps Engineer},
  pdfkeywords={Data Engineering, MLOps, Machine Learning, Cloud Platforms}
}

% Header
\makecvtitle
\begin{center}
  \vspace{-0.5em}
  \textcolor{gray}{\footnotesize Cloud Data Platforms \quad|\quad MLOps \quad|\quad Data Engineering \quad|\quad Machine Learning \& AI}
  \vspace{2em}
\end{center}

% Profile
\section{Profile}

Senior Data Platform \& MLOps Engineer with a track record of building data
systems from the ground up and guiding them into fully automated,
production-grade platforms. My career began at the intersection of econometrics
and software engineering as a freelance developer, progressed into data science
and advanced analytics, and has since evolved into leading machine learning and
MLOps initiatives at scale.

\vspace{0.5em}

I bring a unique blend of engineering craftsmanship and quantitative expertise,
backed by an MSc with a solid econometric background. Whether designing
architectures, operationalizing ML, or mentoring teams, I focus on turning
complex data problems into solutions that deliver long-term value.

\vspace{0.5em}

Academic excellence (both theses graded 9/10) underscores a commitment to
precision, while open-source contributions and continuous learning reflect my
drive to stay ahead in a rapidly changing field.

% Experience
\newpage

\section{Experience}

\cventry{Sep 2024 -- Present}{Senior Cloud Data Platform \& MLOps Engineer}{DELTA Fiber}{Schiedam, Netherlands}{}{
  \vspace{0.1em}
  Shaping the company's cloud-native data platform as a lead engineer and
  principal driver of its strategy, embedding modern MLOps practices to ensure
  scalability, reliability, and long-term value. \\Operating at the intersection
  of infrastructure, data engineering, and applied machine learning, I guide
  teams and stakeholders toward automated, production-ready solutions that
  deliver tangible impact across the organization.
  \vspace{0.75em}
  \begin{itemize}\itemsep0.2em
    \item Spearheaded the evolution of enterprise-wide data solutions, among
          which streaming solutions, increasing analytical efficiency and reducing
          deployment friction.
    \item Architected and maintained AI-enabled systems, including ML models,
          APIs, and end-to-end data pipelines, ensuring robustness and operational
          reliability.
    \item Implemented MLOps best practices: continuous \\integration/deployment
          for ML models, monitoring, alerting, and model lifecycle management to
          guarantee production stability.
    \item Led development of scalable scrapers, crawlers, and interactive
          visualization platforms, expanding data accessibility and enabling faster,
          data-driven decision-making.
  \end{itemize}}

\cventry{Nov 2021 -- Aug 2024}{Senior Machine Learning Engineer}{DELTA Fiber}{Schiedam, Netherlands}{}{
  \vspace{0.1em}
  Took ownership of the company's machine learning stack, ensuring models were
  not just experimental prototypes but reliable, monitored, and continuously
  improving production assets. Collaborated with business units to deliver
  insights and predictive capabilities that shaped strategic decision-making.
  \vspace{0.75em}
  \begin{itemize}\itemsep0.2em
    \item Led integration of machine learning models into production systems.
    \item Built and maintained scalable pipelines and automated workflows.
    \item Supported data-driven decision-making with advanced analytics and visualizations.
  \end{itemize}}

\cventry{Nov 2018 -- Oct 2021}{Data Scientist/Engineer}{DELTA Fiber}{Schiedam, Netherlands}{}{
  \vspace{0.1em}
  Pioneered the company's advanced analytics journey by establishing its first
  modern data infrastructure and operational machine learning pipelines.
  Balanced the dual role of data scientist and engineer, laying the groundwork
  for scalable platforms that later became critical to the business.
  \vspace{0.75em}
  \begin{itemize}\itemsep0.2em
    \item Designed and deployed the first company-wide data warehouse and ETL processes.
    \item Delivered initial advanced analytics solutions, including \\predictive models and automated APIs.
    \item Established CI/CD practices for data science and engineering workflows.
    \item Created scrapers, crawlers, and BI dashboards to improve \\operational visibility.
  \end{itemize}}

\cventry{Sep 2012 -- Aug 2018}{Freelance Developer}{Private Clients}{Apeldoorn, Netherlands}{}{
  \vspace{0.1em}
  Independent developer combining econometric modelling with full-stack web
  solutions for a variety of clients. This role honed my ability to translate
  mathematical concepts into practical applications and gave me hands-on
  experience with diverse stacks, architectures, and deployment strategies.
  \vspace{0.75em}
  \begin{itemize}\itemsep0.2em
    \item Built and deployed full-stack web applications and APIs across multiple frameworks.
    \item Developed econometric modelling solutions to support research and business cases.
    \item Applied statistical modelling and data analysis in client-focused projects.
    \item Gained experience with distributed systems, containerization, and
          automation before moving into large-scale enterprise \\environments.
  \end{itemize}}

\vspace{0.75em}

\cventry{2010 -- 2011}{Commercial Insurance Agent}{Achmea}{Apeldoorn, Netherlands}{}{
  \vspace{0.01em}
  \begin{itemize}
    \item Worked in sales and advisory for commercial insurance products.
  \end{itemize}}

% Skills
\newpage

\section{Skills}

\cventry{}{\textbf{Programming}}{}{}{\textit{Selection of stacks and languages I have worked with:}}{
  \begin{itemize}\itemsep0.2em
    \item \textbf{Python}, R, Rust, Scala, \textbf{Go}, Git \textit{(VCS)}, MATLAB, \textbf{TypeScript},
          React, Next.js, NestJS, Svelte, \textbf{FastAPI}, \textbf{TensorFlow}, \textbf{PyTorch},
          Remote/Containerized Development, Asynchronous \& Threadsafe Programming,
          Test \& Software Design
  \end{itemize}
}

\vspace{0.5em}

\cventry{}{\textbf{Data Engineering \& MLOps}}{}{}{\textit{Selection of tools and concepts I have worked with:}}{
  \begin{itemize}\itemsep0.2em
    \item \textbf{Databricks} \textit{(every feature)}, \textbf{MLflow}, \textbf{dbt}, \textbf{Kafka}, Flink,
          PySpark, Polars, \textbf{Airflow}, Dagster, DuckDB, *NIX, Bash, SQL/NoSQL, ETL/ELT,
          APIs \textit{(REST/GraphQL)}, DWH \& Data Lakehouse Design
  \end{itemize}
}

\vspace{0.5em}

\cventry{}{\textbf{CI/CD \& IaC}}{}{}{\textit{Selection of solutions I am experienced with:}}{
  \begin{itemize}\itemsep0.2em
    \item GitHub Actions, Azure Pipelines, \textbf{Kubernetes}, \textbf{Docker}, Helm, \textbf{Terraform}
  \end{itemize}
}

\vspace{0.5em}

\cventry{}{\textbf{Advanced Analytics}}{}{}{\textit{Some of my advanced analytics expertise:}}{
  \begin{itemize}\itemsep0.2em
    \item \textbf{Machine Learning} \textit{(all algorithms)}, \textbf{Deep Learning},
          Reinforcement Learning, \textbf{LLMs} \textit{(fine-tuning, inference \& deployment)},
          Econometric Modeling, Time Series Analysis, Stata
  \end{itemize}
}

\vspace{0.5em}
\cventry{}{\textbf{Visualization}}{}{}{\textit{Some visualization and dashboarding tools I have worked with:}}{
  \begin{itemize}\itemsep0.2em
    \item \textbf{Power BI}, \textbf{Grafana}, Plotly, Seaborn, Databricks
          Dashboards, Matplotlib, ggplot2, \textbf{Tableau}
  \end{itemize}
}

\vspace{0.5em}

\cventry{}{\textbf{Communication \& Other}}{}{}{\textit{Some miscellaneous skills that add value:}}{
  \begin{itemize}\itemsep0.2em
    \item \textbf{Effective Communication}, Translating Business Requirements to
          Profitable Solutions, LaTeX, Academic Writing
  \end{itemize}
}

% Education
\newpage

\section{Education}

\cventry{2016 -- 2018}{MSc Banking \& Finance}{Utrecht University}{Utrecht, Netherlands}{}{
  \begin{itemize}\itemsep0.2em
    \item Focus on quantitative finance, econometrics, and investment management.
    \item Thesis on machine learning \& econometrics \textit{(\textbf{graded 9/10})}.
  \end{itemize}}

\cventry{2012 -- 2015}{BSc Economics \& Business Economics}{Utrecht University}{Utrecht, Netherlands}{}{
  \begin{itemize}\itemsep0.2em
    \item Customized programme emphasizing econometrics, statistics, and finance.
    \item Thesis graded \textit{\textbf{9/10}}.
  \end{itemize}}

\cventry{2011}{International Business and Management Studies}{Avans University of Applied Sciences}{Breda, Netherlands}{}{
  \begin{itemize}\itemsep0.2em
    \item Propaedeutic obtained \textit{\textbf{in half a year}}.
  \end{itemize}
}
\cventry{2004 -- 2010}{Pre-University Education (VWO)}{Edison College}{Apeldoorn, Netherlands}{}{
  \begin{itemize}\itemsep0.2em
    \item Science \& Technology Profile
  \end{itemize}
}

% Certifications
\section{Certifications}

\cventry{2024}{Dagster \& dbt}{Dagster Labs}{}{}{\textit{Dagster Essentials, Dagster \& dbt integration}}
\cventry{2023}{NestJS Fundamentals \& Authentication}{NestJS}{}{}{}
\cventry{2017}{Applied Data Science (R \& Python)}{DataCamp}{}{}{\textit{ARIMA Modelling, Intermediate R \& Python, Time Series with xts \& zoo}}

\end{document}
